\begin{problem}{Cats Transport}{stdin}{stdout}{2 seconds}{256 megabytes}

Zxr960115 is owner of a large farm. He feeds $m$ cute cats and employs $p$ feeders. There's a straight road across the farm and $n$ hills along the road, numbered from 1 to $n$ from left to right. The distance between hill $i$ and $(i-1)$ is $d_i$ meters. The feeders live in hill 1.

One day, the cats went out to play. Cat $i$ went on a trip to hill $h_i$, finished its trip at time $t_i$, and then waited at hill $h_i$ for a feeder. The feeders must take all the cats. Each feeder goes straightly from hill 1 to $n$ without waiting at a hill and takes all the \textbf{waiting} cats at each hill away. Feeders walk at a speed of 1 meter per unit time and are strong enough to take as many cats as they want.

For example, suppose we have two hills $(d_2 = 1)$ and one cat that finished its trip at time 3 at hill 2 $(h_1 = 2)$. Then if the feeder leaves hill 1 at time 2 or at time 3, he can take this cat, but if he leaves hill 1 at time 1 he can't take it. If the feeder leaves hill 1 at time 2, the cat waits him for 0 time units, if the feeder leaves hill 1 at time 3, the cat waits him for 1 time units.

Your task is to schedule the time leaving from hill 1 for each feeder so that the sum of the waiting time of all cats is minimized.

\InputFile
The first line of the input contains three integers $n, m, p$ $(2 \leq n \leq 10^5, 1 \leq m \leq 10^5, 1 \leq p \leq 100)$.

The second line contains $n-1$ positive integers $d_2, d_3, \dots, d_n$ $(1 \le d_i < 10^4)$.

Each of the next $m$ lines contains two integers $h_i$ and $t_i$ $(1\leqh_i\leqn, 0\leqt_i\leq10^9)$.


\OutputFile
Output an integer, the minimum sum of waiting time of all cats.

Please, do not write the \texttt{\%lld} specifier to read or write 64-bit integers in ะก++. It is preferred to use the \texttt{cin}, \texttt{cout} streams or the \texttt{\%I64d} specifier.


\Examples

\begin{example}
\exmp{4 6 2
1 3 5
1 0
2 1
4 9
1 10
2 10
3 12
}{3
}%
\end{example}

\end{problem}
